Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2023-01-19 reports/supplement/supplement_0.9.1.Rmd
changes supplement

The rate of change in population densities is given by the per capita growth rate - per capita death rate, multipled by population size ([Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x)). Growth rate is the growth rate in absence of any inhibition multiplied by the amount of inhibition.

@@

Taken together, at low amounts of trait variation the diversity effects were driven entirely by the most tolerant strain, in line with a sampling effect. At medium to high trait variation, however, both tolerant and less tolerant strains affected the results in many combinations. The reason was that in the two groups of sulfur bacteria the trade-off between tolerance and growth rate had ecosystem-level effects, i.e. effects on the sulfide concentration and therefore on the cyanobacteria.

>>>>

The rate of change in population densities is given by the per capita growth rate - per capita death rate, multiplied by population size ([Bush et al 2017](https://www.nature.com/articles/s41467-017-00912-x)). Growth rate is the growth rate in absence of any inhibition multiplied by the amount of inhibition.

@@

Taken together, at low amounts of trait variation the diversity effects were driven entirely by the most tolerant strain, in line with a sampling effect. At medium to high trait variation, however, in most combinations both tolerant and less tolerant strains contributed to the diversity effects on tipping point positions or coexistence patterns. The reason was that in the two groups of sulfur bacteria the trade-off between tolerance and growth rate had ecosystem-level effects, i.e. effects on the sulfide concentration and therefore on the cyanobacteria.
